---
title: "2864assignment1"
author: "Yufei xia"
date: "2019/1/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question1

```{r cars}
#search the package 
search()
#find the package and normal distribution use object function 
objects("package:stats",pattern = "norm")
?rnorm 
?qqnorm
#generate 100 random numbers according to normal distribution with mean = 0 stardard deviation = 1
x = rnorm(100)
#qqnorm is a generic function the default method of which produces a normal QQ plot of the values in y,and compare the theoritical quantile with pratical quantile.
qqnorm(x)


```
the rnorm(100) generate 100 random numbers according to normal distribution with mean = 0 stardard deviation = 1.
the qqnorm(x) is a generic function the default method of which produces a normal QQ plot of the values in x,and compare the theoritical quantile with pratical quantile.



## Question2
(a)
```{r}
#sum of 100 number using sum function 

x = sample(1:100)
sum1 = sum(x)
#sum of 100 numbers using for loop 
#set 0 initially
sum2 = 0
for (i in 1:100){
  sum2 = sum2 + x[i]
}
print("the first sum is")
sum1 
print("the second sum is")
sum2
```
the for loop and sum function get the same result.

(b)
```{r}
#genelize 100 number form 1 to the 100
x=sample(1:100)
#get the smallest using the min function
min1 = min(x)
#get the smallest using the for loop
min2 = x[1]
for(i in 2:100){
  if(min2>x[i]){
    min2=x[i]
  }
}
print("the first min is")
print(min1)
print("the second min is")
print(min2)




```
the for loop and the min function get the same result.





##question3 
```{r}
#intilize the sum and sum1 being the 4 elements vector.
n = c(10,20,30,40)
sum =c(0,0,0,0)
sum1 =c(0,0,0,0)
#using the for loop to calculate 
for(i in 1:4){
  for(j in 0:n[i]){
    sum[i]= sum[i]+1.05^j
  }
}
sum
#using the formula to calculate the sum of 
for(i in 1:4){
  sum1[i]=(1-1.05^(n[i]+1))/(1-1.05)
}
sum1
```
this show that the for loop and equation get the same results.

##question4
```{r}
#set up each individual columns
c1 <- c(1:8);
c2 <- c(rep(1,4),rep(2,4))
c3 <- c(rep(1,2),rep(2,2),rep(1,2),rep(2,2))
c4 <- c(rep(1:2,4))
 #using cbind to combine all the columns together
cbind(c1,c2,c3,c4)
```
##question5

```{r}
#find third row 
Formaldehyde[3,]
#5(b)
#find carb column
Formaldehyde$carb
#5(c)
#ploy with x-axis is carb, y-axis is optden
plot(Formaldehyde$carb,Formaldehyde$optden)

```
from the plot we can see that there is an obvious relation between carb and optden in the formaldehyde graph.

##question6
```{r}
#Determine the number of rows and columns for this data frame. 
library(MASS)
nrow(Pima.tr)
ncol(Pima.tr)
print("the median of different columns is")
#set different columns as vectors
x1=Pima.tr[,1]
x2=Pima.tr[,2]
x3=Pima.tr[,3]
x4=Pima.tr[,4]
x5=Pima.tr[,5]
x6=Pima.tr[,6]
x7=Pima.tr[,7]
#calculate median of each column
median(x1)
median(x2)
median(x3)
median(x4)
median(x5)
median(x6)
median(x7)
print("the bmi for different type is as followed")
mean(Pima.tr$bmi[Pima.tr$type =="Yes"])
mean(Pima.tr$bmi[Pima.tr$type =="No"])
```
a)the number of row in this graph is 200, the number of column in this graph is 8.
b)the median of each column is 
c)the bmi for the people test yes for diabete is 34.70,and the bmi for the people who test no for diabete is 31.07
which means that the more bmi index you have, the more chance you get diabetes


##question7
```{r}
Cars93
#find the number of columns
ncol(Cars93)
#find the columns names
colnames(Cars93)
#find the weight as vector of name "weight"
weight=Cars93$Weight
q=cut(weight,c(0,2500,3500,Inf))
#seperate the different stardard.
cars.size=factor(q,labels=c("small","medium","large"))
#add new column
cbind(Cars93,cars.size)
#calculate each mean with small, medium and large sizees of cars
mean(Cars93$MPG.city[cars.size =="small"])
mean(Cars93$MPG.city[cars.size =="medium"])
mean(Cars93$MPG.city[cars.size =="large"])

```
c)the result show that the larger the carsize is, the less MPG it is.