---
title: "hello"
author: "Yufei xia"
date: '2019-02-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##question 1
```{r cars}
help('scan')
data_frameA<-data.frame(name =c("john","lily"),character = c("male","female"), weight = c(72,65))
vectorB<-c(1,2,3,4)
write.table(data_frameA,"dataA")
write(vectorB,"vectorB")
read_A = read.table("dataA")
read_A 
data_frameA
read_B = scan("vectorB")
read_B
vectorB
#after print we can easily see the contents in yhe files are same as in vector and data.frame

```
we get the same data.frame and same vector.

## question 2

```{r pressure, echo=FALSE}
?dump
?save
#Dump takes a vector of names of R objects and produces text representations of the objects on a file or connection,a dump file can usually be sourced into another R session. Save writes an external representation of R objects to the specified file,the objects can be read back from the file at a later date by using the function load or attach . so they are similar in both are present for R objects, the difference between them is that dump could be a source but save is doing rade back.
Biu1=c(1:5)
Biu2=c(6:10)
dump(c("Biu1","Biu2"),file="Biu3")
file.rename("Biu3","Biu4")
Pa1=c(1:7)
Pa2=c(7:13)
save(Pa1,Pa2,file="Pa3")
file.rename("Pa3","Pa4")
?source
?load
remove(Biu1,Biu2)
remove(Pa1,Pa2)
source("Biu4")
Biu1
Biu2
load("Pa4")
Pa1
Pa2
#after "dump" and "save" , if we remove the object we can get them back by source and load and it is same as the objects we created.



```
Dump takes a vector of names of R objects and produces text representations of the objects on a file or connection,a dump file can usually be sourced into another R session. Save writes an external representation of R objects to the specified file,the objects can be read back from the file at a later date by using the function load or attach . so they are similar in both are present for R objects, the difference between them is that dump could be a source but save is doing rade back.
after "dump" and "save" , if we remove the object we can get them back by source and load and it is same as the objects we created.

##question 3
```{r}
## question 3 
z =numeric()
x = runif(1000000) 
y = runif(1000000)
plot(x,y)
lines(seq(0,1,by=0.000001),sqrt((1/2)^2-(seq(0,1,by=0.000001)-(1/2))^2),col=2)
z=((x-(1/2))^2+(y-(1/2))^2<(1/2)^2)*4
pi.estimate=mean(z)
print("the pi estimate is")
pi.estimate
print("the varience is")
var(z)
print("the confidence interval is")
confidenceinterval=c(pi.estimate+1.96*sqrt(var(z))/sqrt(1000000),pi.estimate-1.96*sqrt(var(z))/sqrt(1000000))
confidenceinterval



```
##question 4 
```{r}
#a
g300 = chickwts[chickwts$weight>300,]
g300
#b
linsed = chickwts[chickwts$feed=="linseed",]
linsed
#c
mean(linsed$weight)
#d
nonlinsed = chickwts[chickwts$feed!="linseed",]
mean(nonlinsed$weight)


```


##question 5
```{r}
library(MASS)
#combine
Pima=rbind(Pima.tr,Pima.te)
#check
p=all(rbind(Pima.tr,Pima.te)==Pima)
p
#seprate different standard
z=cut(Pima$bmi,c(0,15,16,18.5,25,30,35,40,Inf))
#label them
levels(z)=c("Very severely underweight","Severely underweight","Underweight","Normal","Overweight","Obese Class I","Obese Class II","Obese Class III")
table(z)
plot(z)
y=cut(Pima$bmi,c(0,18.5,25,Inf))
levels(y)=c("underweight","normal","overweight")
table(y)
plot(y)
```
#according to the barplot, it tells us only a few persons are underweight and the majority people are overweight, the number of normal weight persons are ok.


##question6 
```{r}
#Question6
#a
#use lm function
h=lm(cars$dist~cars$speed,data=cars)
summary(h)
coefficient=coef(h)
#b
#use coefficient
D.hat=coefficient[1]+coefficient[2]*cars$speed
residuals=cars$dist-D.hat
residuals
summary(residuals)
#comment:it is same as the part a.
#c
#plot 
boxplot(residuals,ylab="residuals")
#plot
hist(residuals)
#comment:histplot give us the good plot with group of distribution on variables,but boxplot give the most important line from the group.
#d
#plot qqnorm
qqnorm(residuals)
#plot qqline
qqline(residuals)
#comment:qqline plot one exace line based on qqnorm.qqline can illustrate the approximate look of qqnorm.They are linearly dependent.

```
since the residuals are lined well on the straight line, it indicates that the residuals are normally distributed




